Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
wesley updates
added some stuff

For $k = 1, 2, \ldots$ we have 
\[u_{n+1}^{k+1} = g_{\Delta t} (t_n, u_n^{k+1}) + \big(
g_{\textnormal{fine}}(t_n, u_n^k) - g_{\Delta t}(t_n, u_n^k). \]

@@

FROM THE SLIDES

ASHI carry?

@@

\subsection{Expectations}
TODO WESLEY
\subsection{General Remarks about Results}
One of the TODO WESLEY

@@

\[
y'(t) = f(t, y) = \lambda y, \, y(0) = 1
\]
\[
y''(t) + 2y'(t) + 5y(t) = 0, \, y(0) = 1 \, y'(0) = 0.
\]

>>>>

For $k = 1, 2, \ldots$ we have 
\[u_{n+1}^{k+1} = g_{\Delta t} (t_n, u_n^{k+1}) + \big(
g_{\textnormal{fine}}(t_n, u_n^k) - g_{\Delta t}(t_n, u_n^k)\big). \]

@@

Let us consider the ODE $du/dt = \lambda u$. Let $g_{\textnormal{fine}}(t_n,
u_n) = \bar{g_{\textnormal{fine}}}u_n$ and $g_{\Delta t}(t_n, u_n) =
\bar{g_{\Delta t}} u_n$. As shown by Staff et al. [cite], the parareal method
becomes

\[ u_n^k = \left( \sum_{j=0}^k {n \choose j} (\bar{g_{\textnormal{fine}}} -
g_{\Delta t})^j \bar{g_{\Delta t}}^{n-j} \right) u_0 = H(\bar{g_{\Delta
t}}, \bar{g_{\textnormal{fine}}}, n, k, \lambda)u_0 \]

This is stable if $\textnormal{max}_{n, k} |H| \leq 1$.

When $\lambda \in \mathbb{R}$ and $\lambda \leq 0$, Staff et. al also show that

\[
    \begin{aligned}
    |H| &\leq \sum_{j=0}^n {n \choose j} |\bar{g_{\textnormal{fine}}} -
    g_{\Delta t}|^j |\bar{g_{\Delta t}}|^{n-j} \\
    &= (|\bar{g_{\textnormal{fine}}} - g_{\Delta t}| + |\bar{g_{\Delta
    t}}|)^n \leq 1
    \end{aligned}
\]

To satisfy these conditions, we have that 
\begin{enumerate}
    \item $| \bar{g_{\textnormal{fine}}} | \leq 1$: This is the usual stability
        requirement.
    \item $|\bar{g_{\textnormal{fine}}} - 2 \bar{g_{\Delta t}}| \leq 1$.
\end{enumerate}

@@

\subsection{Expectations}
TODO WESLEY

\subsection{General Remarks about Results}
LETS SEE IF I HAVE TO DISCLAIM ANY GLOBAL FAILURES IN OUR RESULTS

@@

\[
y'(t) = f(t, y) = \lambda y, \, \, y(0) = 1
\]
\[
y''(t) + 2y'(t) + 5y(t) = 0, \, \, y(0) = 1, \, y'(0) = 0.
\]
